Constructing the transition graphs of interacting hysterons

### 2022-06-02 Paper_draft.tex
Changed instance of 'all-zero/all-one states' to 'saturated states'

A well-defined transition graph for $N$ hysterons consists out of $2^N$ states, and $2(2^N-1)$ transitions, namely the up transitions for each state except the all-ones state and the down transitions for each state except the all-zero state. A transition graph is constructed by choosing a transition path for each of these $2(2^N-1)$ transitions. A transition path may be a single hysteron flip, or may consist of multiple flipped hysterons. When a transition path consists of multiple hysteron flips, we speak of an avalanche.\\

>>>>

A well-defined transition graph for $N$ hysterons consists out of $2^N$ states, and $2(2^N-1)$ transitions, namely the up and down transitions from each state, except for the saturated states which only have one transition each. A transition graph is constructed by choosing a transition path for each of these $2(2^N-1)$ transitions. A transition path may be a single hysteron flip, or may consist of multiple flipped hysterons. When a transition path consists of multiple hysteron flips, we speak of an avalanche.\\
